cardinalR: Generating interesting high-dimensional data structures

### 2025-11-08 paper-cardinalR.Rmd
Added conclusion sentence

These structures are designed to support not only algorithm diagnostics, but also teaching high-dimensional concepts, benchmarking reproducibility, and evaluating hyperparameter sensitivity. By allowing users to adjust dimensionality, sample size, noise, and clustering properties, the package promotes transparent experimentation and comparative model evaluation.

Future extensions of `cardinalR` may include biologically inspired or application-driven data structures would further broaden its utility in domains such as bioinformatics, forensic science, and spatial analysis.

>>>>

These structures are designed to support not only algorithm diagnostics, but also teaching high-dimensional concepts, benchmarking reproducibility, and evaluating hyper-parameter sensitivity. By allowing users to adjust dimensionality, sample size, noise, and clustering properties, the package promotes transparent experimentation and comparative model evaluation. Together, these capabilities make `cardinalR` a versatile tool for generating interpretable, high-dimensional datasets that advance research, teaching, and evaluation of data-analytic methods.

Future extensions of `cardinalR` may include biologically inspired or application-driven data structures that would further broaden its utility in domains such as bioinformatics, forensic science, and spatial analysis.

### 2025-11-08 paper-cardinalR.tex
Added conclusion sentence

These structures are designed to support not only algorithm diagnostics, but also teaching high-dimensional concepts, benchmarking reproducibility, and evaluating hyperparameter sensitivity. By allowing users to adjust dimensionality, sample size, noise, and clustering properties, the package promotes transparent experimentation and comparative model evaluation.

Future extensions of \texttt{cardinalR} may include biologically inspired or application-driven data structures would further broaden its utility in domains such as bioinformatics, forensic science, and spatial analysis.

>>>>

These structures are designed to support not only algorithm diagnostics, but also teaching high-dimensional concepts, benchmarking reproducibility, and evaluating hyper-parameter sensitivity. By allowing users to adjust dimensionality, sample size, noise, and clustering properties, the package promotes transparent experimentation and comparative model evaluation. Together, these capabilities make \texttt{cardinalR} a versatile tool for generating interpretable, high-dimensional datasets that advance research, teaching, and evaluation of data-analytic methods.

Future extensions of \texttt{cardinalR} may include biologically inspired or application-driven data structures that would further broaden its utility in domains such as bioinformatics, forensic science, and spatial analysis.
